GMSE: an R package for generalised management strategy evaluation

### 2018-05-09 notebook/ms/SI1.Rmd
Reviewer 1 concerns regarding SI1

The predicted consequences of $X_{i,j}$ for resource abundance differ for each possible action. For each action, no consequence is predicted if the policy is not allowed by a simulation of GMSE (e.g., `culling = FALSE`). For allowed actions, the parameter `manager_sense` ($\sigma$) modulates predicted consequences for abundance by some factor; this is useful because not all actions attempted by users will be realised, and a value of $\sigma = 1$ tends to greatly overestimate how much the actions attempted by users will actually translate to a change in resource abundance. In practice, the default $\sigma = 0.1$ performs well. Allowed actions are predicted by managers to have the following effects:

- `scaring` is assumed to be nonlethal and therefore have no effect on resource number.
- `culling` decreases resource number by $\sigma(1 + \lambda)$, where $\lambda$ is the GMSE argument `lambda` that defines the baseline population growth rate of resources.
- `castration` decreases resource number by $\sigma\lambda$.
- `feeding` increases resource number by $\lambda$.
- `help_offspring` increases resource number by $\sigma$.

These effects cannot be altered directly in `gmse` or `gmse_apply` (though parameter values can of course be changed using `manager_sense` and `lambda` arguments), but future versions of GMSE might include different predicted effects to increase precision or allow for multiple resource types or different actions. The summation of $X_{i,j}$ for all actions defines the predicted change in resource abundance caused by the policy of an individual $i$, $\Delta A_{i}$.

>>>>

The predicted consequences of $X_{i,j}$ for resource abundance differ for each possible action. For each action, no consequence is predicted if the policy is not allowed by a simulation of GMSE (e.g., `culling = FALSE`). For allowed actions, the parameter `manager_sense` ($\sigma$) modulates predicted consequences for abundance by some factor; this is useful because not all actions attempted by users will be realised, and a value of $\sigma = 1$ tends to slightly overestimate how much the actions attempted by users will actually translate to a change in resource abundance. In practice, the default $\sigma = 0.9$ performs well. Allowed actions are predicted by managers to have the following effects (again, we emphasise that whether or not these effects are realised will depend later on the user model, to which the manager does not have access):

- `scaring` is assumed to be nonlethal and therefore have no effect on resource number (resources are moved to a random cell on the landscape, as sampled from a uniform distribution such that movement to any given cell is equally probable).
- `culling` decreases resource number by $\sigma$.
- `castration` decreases resource number by $\sigma\lambda$, where $\lambda$ is the GMSE argument `lambda` that defines the baseline population growth rate of resources.
- `feeding` increases resource number by $\sigma\lambda$.
- `help_offspring` increases resource number by $\sigma$.

Note that $\sigma$ is included in all of the predicted actions above as a modulator for how strongly the manager predicts users will respond to a change in manager policy (e.g., a value of 0 would predict no reaction on the part of users to a change in policy, while a value of 1 would predict that an action would increase in exact proportion to its decrease in cost). These effects cannot be altered directly in `gmse` or `gmse_apply` (though parameter values can of course be changed using `manager_sense` and `lambda` arguments), but future versions of GMSE might include different predicted effects to increase precision or allow for multiple resource types or different actions. The summation of $X_{i,j}$ for all actions defines the predicted change in resource abundance caused by the policy of an individual $i$, $\Delta A_{i}$.

### 2018-05-09 notebook/ms/ms.Rmd
Reviewer 1 concerns regarding SI1

Overall, a single call of the genetic algorithm simulates the process of thinking and decision-making for one manager or user. In each new call of the genetic algorithm, a unique population of temporary manager or user strategies is initialised. In each iteration of the genetic algorithm, these strategies crossover and mutate; when this results in strategies that are over-budget, expenditures are iteratively decreased at random until budget constraints are satisfied. A fitness function then evaluates each strategy in the population, and a tournament is used to select the next iteration of strategies [@Hamblin2013]. The genetic algorithm terminates when a minimum number of iterations has passed and the increase in the fitness of the fittest strategy between the current and previous iteration is below some threshold. The highest fitness strategy in the population then becomes the stakeholder's new strategy.

@@

|  scaring        |  FALSE  | Resource scaring is a policy option                                                              |
|  culling        |  TRUE   | Resource culling is a policy option                                                              |
|  castration     |  FALSE  | Resource castration is a policy option                                                           |
|  feeding        |  FALSE  | Resource feeding (increases lambda) is a policy option                                           |
|  help_offspring |  FALSE  | Resource helping (increases offspring number) is a policy option                                 |

>>>>

A single call of the genetic algorithm simulates the process of thinking and decision-making for one manager or user. In each new call of the genetic algorithm, a unique population of temporary manager or user strategies is initialised. In each iteration of the genetic algorithm, these strategies crossover and mutate; when this results in strategies that are over-budget, expenditures are iteratively decreased at random until budget constraints are satisfied. A fitness function then evaluates each strategy in the population, and a tournament is used to select the next iteration of strategies [@Hamblin2013]. The genetic algorithm terminates when a minimum number of iterations has passed and the increase in the fitness of the fittest strategy between the current and previous iteration is below some threshold. The highest fitness strategy in the population then becomes the stakeholder's new strategy.

@@

|  scaring        |  FALSE  | Resource scaring (moves a resource to a random landscape cell) is a policy option                |
|  culling        |  TRUE   | Resource culling (removes a resource entirely) is a policy option                                |
|  castration     |  FALSE  | Resource castration (sets a resource's lambda to zero) is a policy option                        |
|  feeding        |  FALSE  | Resource feeding (increases a resource's lambda) is a policy option                              |
|  help_offspring |  FALSE  | Resource helping (increases a resource's offspring number) is a policy option                    |
